### 2022-03-30 about/vita.tex
It is 2022 omg
New paper

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4. Thesis topic: ``Structural properties of Galton--Watson trees.''
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\papercount=3
\pubbegin P
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. To appear in {\sl Discrete Mathematics
and Theoretical Computer Science}, 11~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\endgroup

>>>>

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4.
Thesis: ``Structural properties of conditional Galton--Watson trees.''
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

\begingroup\frenchspacing
\papercount=3
\pubbegin P
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl Discrete Mathematics
and Theoretical Computer Science} {\bf 24},1 (2022), \#7, 16~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\endgroup
\endgroup%end the frenchspacing

### 2022-03-30 misc/expo/additive.tex
New paper

\proof Let $X$ be a subspace of $\FF_p^N$ chosen uniformly at random from all subspaces of
codimension $n$, where $n$ will be specified later. Let $q : \FF_p^N \to \FF_p^N/X$ be the
quotient map taking $v$ to $v+X$. Since $q$ is a group homomorphism, its restriction to $A$
is a Freiman homomorphism
of order $k$. The only way that the restriction of $q$ to $A$ can fail to be a {\it $k$-isomorphism}
is if there exist $a_1,\ldots,a_k,b_1,\ldots,b_k\in A$ such that $a_1+\cdots+a_k \ne b_1+\cdots+b_k$
but $q(a_1)+ \cdots + q(a_k) = q(b_1)+\cdots+q(b_k)$. This is equivalent to
$a_1+\cdots+a_k - b_1-\cdots-b_k$ being in $X$. For any nonzero $y\in \FF_p^N$, we have
$$\pr\{y\in X\} = {p^{n-n}-1\over p^N-1} < {1\over p^n},$$
and since $|kA-kA|\le C|A|$,
$$\pr\biggl\{\bigcup_{y\in (kA-kA)\setminus\{0\}} \{y\in X\}\biggr\} \le \sum_{y\in (kA-kA)\setminus 0}
\pr\{y\in X\} < {C|A|\over p^n},$$
the probability that $q$ is a $k$-isomorphism is nonzero so long as $p^n\ge C|A|$. Taking the minimal such $n$,
we have $p^{n-1} < C|A|$ and
can conclude there is a subspace $X$ of dimension $n$ that contains a set $k$-isomorphic to $A$.\slug

>>>>

\proof Let $X$ be a subspace of $\FF_p^N$ chosen uniformly at random from all subspaces of
codimension $n$, where $n$ will be specified later. Let $q : \FF_p^N \to \FF_p^N/X$ be the
quotient map taking $v$ to $v+X$. Since $q$ is a group homomorphism, its restriction to $A$
is a Freiman homomorphism
of order $k$. The only way that the restriction of $q$ to $A$ can fail to be a {\it $k$-isomorphism}
is if there exist $a_1,\ldots,a_k,b_1,\ldots,b_k\in A$ such that $a_1+\cdots+a_k \ne b_1+\cdots+b_k$
but $q(a_1)+ \cdots + q(a_k) = q(b_1)+\cdots+q(b_k)$. This is equivalent to
$a_1+\cdots+a_k - b_1-\cdots-b_k$ being in $X$. For any nonzero $y\in \FF_p^N$, we have
$$\pr\{y\in X\} = {p^{N-n}-1\over p^N-1} < {1\over p^n},$$
and since $|kA-kA|\le C|A|$,
$$\pr\biggl\{\bigcup_{y\in (kA-kA)\setminus\{0\}} \{y\in X\}\biggr\} \le \sum_{y\in (kA-kA)\setminus 0}
\pr\{y\in X\} < {C|A|\over p^n},$$
the probability that $q$ is a $k$-isomorphism is nonzero so long as $p^n\ge C|A|$. Taking the minimal such $n$,
we have $p^{n-1} < C|A|$ and
can conclude there is a subspace $X$ of dimension $n$ that contains a set $k$-isomorphic to $A$.\slug

Next, we will prove an embedding lemma for subsets of $\ZZ$. In this setting the ``simpler'' group
that we pass to is a cyclic group, but first we need a lemma that essentially says that passing
to a cyclic group preserves the additive structure.

\proclaim Lemma {\advthm}. Let $k$ and $n$ be positive integers and let $A\subseteq \ZZ$ be a set of
diameter less than $n/k$; i.e., $\max A - \min A < n/k$. Then the map $\phi : A\to \ZZ_n$ that
sends $a\mapsto a\bmod n$ is a Freiman isomorphism of order $k$.

\proof The function $\phi$ is the restriction of a group homomorphism to $A$, so it is a Freiman
homomorphism of every order. Now suppose that $\min A = r$ and $\max A = s$, so that $s-r < n/k$.
Then if $a_1,\ldots,a_k,b_1,\ldots,b_k$ are such that $\phi(a_1)+\cdots+\phi(a_k) = \phi(b_1)+\cdots+\phi(b_k)$,
then $a_1+\cdots+a_k -b_1-\cdots-b_k$ is at most $k(s-r) < n$ but also a multiple of $n$.
Hence this difference is zero and $a_1 + \cdots + a_k = b_1+\cdots+b_k$.\slug

As promised, here is the embedding lemma for subsets $A\subseteq \ZZ$. This time, we cannot simply
say anything about the whole set $A$, but we can about a large subset of it.

\parenproclaim Lemma {\advthm} (Ruzsa embedding lemma in $\ZZ$). Let $k\in \NN$ and $C\in \RR$.
If $A\subseteq \ZZ$ with $|kA-kA|\le C|A|$, then there exists $A'\subseteq A$ with $|A'|\ge |A|/k$
such that $A'$ is $k$-isomorphic to a subset of $\ZZ/N\ZZ$, where $N$ is a prime between
$2C|A|$ and $4C|A|$.\slug

\proof It is easily checked that translation is a Freiman isomorphism of every order, so we may assume
that $A\subseteq \NN_0$. Let $p$ be a prime bigger than $k\max A$ and consider the
sequence of functions
$$\ZZ \buildrel{q_1}\over\longrightarrow \ZZ_p \buildrel{\mu_r}\over\longrightarrow \ZZ_p
\buildrel\iota\over\longrightarrow \ZZ \buildrel{q_2}\over\longrightarrow \ZZ_N,$$
where $q_1$ is reduction modulo $p$, $\mu_r$ is multiplication by a random nonzero element $r\in \ZZ_p$,
$\iota$ takes an element of $\ZZ_p$ to its representative in $[0,p)$, and $q_2$ is reduction mod $N$.
The only map here that is not a group homomorphism is $\iota$, so to show that the composition
$\phi = q_2\circ \iota\circ \mu_r\circ q_1$ restricted to $A$ is a $k$-homomorphism, it suffices to worry
about $\iota$. Split the interval $\{0,1,\ldots,p-1\}$ into $k$ subintervals $J_1,\ldots,J_k$,
each of diameter less than $p/k$ and let $I_j = \iota^{-1}(J_j)$ for each $1\le j\le k$. By the previous
lemma, the map $\iota^{-1}$ restricted to any $J_j$ is a $k$-isomorphism, so $\iota$ restricted
to $I_j$ is a $k$-isomorphism as well. Now let
$$A_{j,r} = \bigl\{a\in A : \mu_r\bigl(q_1(a)\bigr) \in I_j\bigr\}$$
and note that $\mu_r\bigl(q_1(a)\bigr) = ra \bmod p$. Thus the composition $\phi$ is a $k$-homomorph\-ism
when restricted to any $A_{j,r}$.

We shall now show that with positive probability, the restriction of $\phi$ to every $A_{j,r}$ is
a $k$-isomorphism. For fixed $r$, the restriction to $A_{j,r}$ is not a $k$-isomorphism
if there exist $j$ and $a_1,\ldots,a_k,b_1,\ldots,b_k\in A_{j,r}$ such that
$a_1+\cdots+a_k \ne b_1+\cdots+b_k$ but $\phi(a_1)+\cdots+\phi(a_k) = \phi(b_1)+\cdots+\phi(b_k)$.
